Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2016-04-06 contents/introduction.tex
adds more citations

Statistical Deformable Models (SDMs) of various object classes is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}. Recently, we have witnessed tremendous developments on SDMs of human faces and bodies trained with images that are captured under unconstrained conditions, usually referred to as ``in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014, kazemi2014one, zhu2015face, antonakos2015feature, antonakos2015active, Joan_cvpr2015, tzimiropoulos2015project}. This is attributed to:
\begin{itemize}
\item The abundance of complex visual data, spread through web services (e.g. Youtube, Flickr, Google Images), which has led to the development of ``in-the-wild" databases of human faces and bodies \cite{Belhumeur2011, Le2012, Zhu2012, Burgos2013}.

>>>>

Statistical Deformable Models (SDMs) of various objects is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}. Recently, we have witnessed tremendous developments on SDMs of human faces and bodies trained with images that are captured under unconstrained conditions, usually referred to as ``in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014, kazemi2014one, Alabort2014, zhu2015face, antonakos2015feature, antonakos2015active, Joan_cvpr2015, tzimiropoulos2015project}. This is attributed to:
\begin{itemize}
\item The abundance of complex visual data, spread through web services (e.g. Youtube, Flickr, Google Images), which has led to the development of ``in-the-wild" databases of human faces and bodies \cite{Belhumeur2011, Le2012, Zhu2012, Burgos2013}.
